\documentclass[a4paper,12pt]{article}
\usepackage{fullpage}
\usepackage{url}

\begin{document}
\title{Example BibTeX File}
\author{Bruce C. Miller \\
{\tt bm3719@gmail.com}}
\date{August 20, 2009}
\maketitle

\section{Introduction}
BibTeX uses an external database of references.  Create one or more \emph{.bib}
files and reference them with the \texttt{\textbackslash bibliography}
command.  This document uses two external files, one with a couple normal
references, and the third with a website reference.

Here's the breakdown of the templates and required fields:

\textbf{@article}
An article from a magazine or a journal.
\begin{itemize}
\item Required fields: author, title, journal, year.
\item Optional fields: volume, number, pages, month, note.
\end{itemize}

\textbf{@book}
A published book
\begin{itemize}
\item Required fields: author/editor, title, publisher, year.
\item Optional fields: volume/number, series, address, edition, month, note.
\end{itemize}

\textbf{@booklet}
A bound work without a named publisher or sponsor.
\begin{itemize}
\item Required fields: title.
\item Optional fields: author, howpublished, address, month, year, note.
\end{itemize}

\textbf{@conference}
Equal to inproceedings
\begin{itemize}
\item Required fields: author, title, booktitle, year.
\item Optional fields: editor, volume/number, series, pages, address, month,
  organization, publisher, note.
\end{itemize}

\textbf{@inbook}
A section of a book
\begin{itemize}
\item Required fields: author/editor, title, chapter and/or pages, publisher, year.
\item Optional fields: volume/number, series, type, address, edition, month,
  note.
\end{itemize}

\textbf{@incollection}
A section of a book having its own title.
\begin{itemize}
\item Required fields: author, title, booktitle, publisher, year.
\item Optional fields: editor, volume/number, series, type, chapter, pages,
  address, edition, month, note.
\end{itemize}

\textbf{@inproceedings}
An article in a conference proceedings.
\begin{itemize}
\item Required fields: author, title, booktitle, year.
\item Optional fields: editor, volume/number, series, pages, address, month,
  organization, publisher, note.
\end{itemize}

\textbf{@manual}
Technical manual
\begin{itemize}
\item Required fields: title.
\item Optional fields: author, organization, address, edition, month, year,
  note.
\end{itemize}

\textbf{@mastersthesis}
Master thesis
\begin{itemize}
\item Required fields: author, title, school, year.
\item Optional fields: type, address, month, note.
\end{itemize}

\textbf{@misc}
Template useful for other kinds of publication
\begin{itemize}
\item Required fields: none
\item Optional fields: author, title, howpublished, month, year, note.
\end{itemize}

\textbf{@phdthesis}
Ph.D. thesis
\begin{itemize}
\item Required fields: author, title, year, school.
\item Optional fields: address, month, keywords, note.
\end{itemize}

\textbf{@proceedings}
The proceedings of a conference.
\begin{itemize}
\item Required fields: title, year.
\item Optional fields: editor, volume/number, series, address, month,
        organization, publisher, note.
\end{itemize}

\textbf{@techreport} 
Technical report from educational, commercial or standardization institution.
\begin{itemize}
\item Required fields: author, title, institution, year.
\item Optional fields: type, number, address, month, note.
\end{itemize}

\textbf{@unpublished}
An unpublished article, book, thesis, etc.
\begin{itemize}
\item Required fields: author, title, note.
\item Optional fields: month, year.
\end{itemize}

\section{Citing Text}
Here's some text that makes use of the various bibliography entries in the
external files \cite{Abedon1994}.  Here's another one
\cite{website:fermentas-lambda}.  Note that the second reference uses a url
which requires an external package.

\bibliographystyle{plain}
\bibliography{bibtex_notes,more_bibtex}


\end{document}
