\documentclass{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\textheight=10in
\pagestyle{empty}
%\raggedbottom
\raggedright

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }
% DEFINITIONS FOR RESUME
\newcommand{\area}[2]{\vspace*{-9pt} \begin{verse}\textbf{#1}   #2 \end{verse}  }
\newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-18pt} \hrulefill \\}
\newcommand{\header}[1]{{\hspace*{-15pt}\vspace*{7pt} \textsc{#1}} \vspace*{-7pt} \lineunder}
\newcommand{\employer}[3]{{ \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }}
\newcommand{\contact}[3]{
\vspace*{-8pt}
\begin{center}
{\LARGE \scshape {#1}}\\
#2 \lineunder
#3
\end{center}
\vspace*{-8pt}
}
\newenvironment{achievements}{\begin{list}{$\bullet$}{\topsep 0pt \itemsep
      -2pt}}{\vspace*{4pt}\end{list}}

\newcommand{\schoolwithcourses}[4]{
\textbf{#1} #2 $\bullet$ #3\\
#4
\vspace*{5pt}
}
% END RESUME DEFINITIONS

\begin{document}

\small
\smallskip
\vspace*{-44pt}

\contact{\textbf{Bruce C. Miller}}
{xxxx Dixie Hill Rd., Apt. xxx $\bullet$ Fairfax, VA 22030}
{(703) xxx-xxxx $\bullet$ bm3719@gmail.com}

\header{Professional Objective} The work I find particularly compelling applies
computer science topics like functional programming, data analytics, and big
data to real world problems on DoD/IC projects hosting research or rapid
prototyping for proof of concept.  Participation in such undertakings allows
full leverage of my experience in software engineering, a personal interest in
functional programming languages, and many years of industry domain knowledge.
\vspace{7pt}

\header{Skills}
\begin{achievements}
\item Actively proficient in Clojure, Python, Common Lisp, Scheme, Emacs Lisp,
  Haskell, SQL, and C.
\item An up-to-date professional focus on big data, data analytics, cloud
  computing, applied programming language theory, and functional programming.
\item Familiarity with relational and non-relational database design, \LaTeX,
  several Unix-variants, GNU Emacs, data visualization, web development, team
  leadership, written/oral presentation, and various markup and scripting
  languages.
\end{achievements}

\header{Work History}

\employer{Whiteboard Federal Technologies}{2014-present}{Principle Software
  Engineer/Tech Lead} Currently working on the Pentagon G2's AICIG project.
Brought in as an SME to construct a team of Clojure programmers and to be the
project's principle architect.
\begin{achievements}
\item Acted as tech lead and occasionally team lead for the project.  Converted
  a small, pre-existing team of 3 non-functional programmers into a team of 6
  Clojure programmers which is still growing.
\item Designed the underlying architecture for all of the software products in
  Clojure.  Confining side effects and maximizing features like testability,
  maintainability, and program correctness were priorities.
\item Prototyped experimental features to demonstrate feasibility.
\item Programmed exclusively in Clojure, using Emacs.
\item Managed regular interaction with government clients and non-technical
  project management.  Conducted all technical interviews.  Managed the
  development schedule.  Experimentally decided upon optimal level of
  development methodology overhead.
\end{achievements}

\employer{Sotera Defense Solutions (formerly Potomac Fusion,
  Inc.)}{2010-2013}{Senior Software Engineer} Employed on a DARPA project
called XDATA, performing research towards developing an analytics framework
that operates against extremely large datasets to be used across all related
DARPA projects.
\begin{achievements}
\item Wrote composable analytics (potentially part of a cloud analytic
  framework), using Clojure and a Clojure EDSL called Cascalog, bringing
  together disparate cloud capabilities (primarily available on JVM languages)
  into a single, unified, functional model.
\item Researched the state of the art in cloud computing and applicability to
  project goals.
\item Wrote large data analytics in Python.
\item Wrote all documentation in \LaTeX.
\end{achievements}
Until Mar 2012, developed cloud analytics at a DARPA project called Nexus7,
which explored analytic capability against extremely large IC datasets, in an
attempt to address seemingly intractable problems illustrated by the war in
Afghanistan.
\begin{achievements}
\item Worked with many cloud technologies, primarily Hadoop (HDFS/MapReduce)
  and Apache Hive, writing and optimizing analytic algorithms within them.
\item Built visualizations via machine learning algorithms within Weka and
  Apache Mahout.
\item Analytics development primarily in Python, HiveQL, and Clojure.
\item Deployed to Afghanistan for 7 months, supporting in-theater operations at
  strategic and tactical levels.  Developed big data solutions against live
  data and gave presentations to military and civilian decision-makers.
\end{achievements}
Until Feb. 2011, was part of an ``Advanced Analytics'' group for project
GlobalWatch, delivering data visualization and analysis tools to the primary IC
agency.
\begin{achievements}
\item Held a principle engineer back-end role wherein the primary mission was
  to create frameworks for anomaly/change detection within live data feeds.
\item Subsumed requisite knowledge of statistical learning models, machine
  learning, and statistics.
\item Software development within the JVM ecology, in Java and Jython.
\item Some front end development in JavaScript, jQuery, Ext JS, and JSP.
\item Build management with Maven and Nexus.
\item Interviewed candidates for senior to junior level development positions.
\item Carried out on-site deployments of releases in South Korea.
\end{achievements}

\employer{iSYS, LLC}{2007-2010}{Senior Software Engineer} Part of a team
responsible for the ``Next Generation'' CODIS (Combined DNA Index System), a
DNA Forensics database and search engine funded by the FBI and used in all
forensic DNA work within the US and 22 foreign countries.
\begin{achievements}
\item Full participation in the software development life cycle for a large
  (over 1 million SLOC), enterprise-grade, distributed application.
\item C\# development, employing the use of design patterns, WCF, LINQ, and
  Parallel Extensions.
\item Database design and development in SQL Server, with stored procedures in
  T-SQL.
\item Led development for several critical features within CODIS, such as
  Pr\"um Treaty support (used by EU nations) and tuning algorithms to meet
  performance goals.
\item Interviewed candidates for senior to junior level development positions.
\end{achievements}

\employer{e-LYNXX Corporation}{2004-2007}{Software Engineer} Responsibilities
included designing and developing components within a large-scale n-tier
application, managing a high volume of government and private sector financial
transactions.
\begin{achievements}
\item Full SDLC participation, including requirements analysis, design,
  development/implementation, debugging, and maintenance.
\item C\# development in Visual Studio 2003/2005, Delphi development in Borland
  Developer Studio 2006, and PL/SQL development in PL/SQL Developer.
\item Database integration with Oracle 8i, 9i, and 10g, writing stored
  procedures, data modeling/remodeling, and using DALs such as Direct Oracle
  Access and ODP.Net.
\item Research and implementation of architecture improvements using various
  design patterns, features of the .Net Framework, and concepts from the
  academic community.
\item Migration and redesign of legacy codebases from Delphi 5 to Delphi 2006
  and C\#.
\item Revision control and change tracking in Borland StarTeam.
\item B2B integration using WebServices, EDI (Electronic Data Interchange), and
  cXML.
\item Design/development of ancillary and supporting Windows services in C\# and
  Delphi 2006.
\item DDL/DML scripts in SQL.
\item Build script management and build deployment.
\end{achievements}

\employer{Inclusive Technology Solutions Inc.}{2005-2007}{Senior Software
  Engineer (part-time)} Acted as a senior member of an IT consulting firm,
where initial responsibilities included the full development process, later
migrating to a project lead role on all n-tier web application/e-commerce
projects with team sizes up to 4.
\begin{achievements}
\item Projects managed and/or implemented involved languages such as C\#,
  ASP.Net, and PHP; scripting in JavaScript; markup in XHTML and HTML; and
  platforms such as Solaris, Linux, and Windows Server.
\item Conducted requirements and design analysis; selecting best platforms,
  technologies, architectures, and structural paradigms.
\item Reviewed all code for best practices, W3C standards compliance, and
  cross-browser compatibility.
\item Database design with MySQL.
\item Coordinated exchange between internal client contacts, junior developers,
  graphic designers, and external contractors.
\item Performed technical interviews for all development and graphic design
  applicants.
\end{achievements}

\employer{C\&L Instruments}{2001-2002}{Software Engineer} Completed development
of a fluorescence imaging data acquisition and analysis application in Visual
C++ 6.0 for use in studying ratio imaging and ion concentration in cellular
biology experiments.
\begin{achievements}
\item Full participation in the software development life cycle, including
  requirements analysis, design, development/implementation, debugging, and
  maintenance.
\item GUI programming in MFC and GDI, including image display, image
  manipulation, and graphical data analysis.
\item Wrote wrappers for numerous proprietary imaging APIs to support various
  manufacturers' digital microscope cameras via a unified user interface.
\item Co-developed device drivers in C++ for in-house expansion cards
  controlling fluorescent microscopes, illuminators, and filter controllers.
\item Assimilated a large amount of domain-specific knowledge regarding
  fluorescent microscopy and biotech research in general.
\end{achievements}

\employer{Mantra Communications}{May 2000 - August 2000}{Software Engineer
  (intern)} Developed an administrative front end in Java for a bandwidth
modification suite, ported various Java and C packages to/from HP-UX and
Solaris, and designed numerous ancillary and internal applications.
\begin{achievements}
\item SDLC participation in detailed design, implementation, debugging, and
  maintenance.
\item Server-side web application programming using JSP, Java Servlets, and
  JavaBeans.
\item Java development in Borland JBuilder.
\item Revision control with CVS.
\item Database integration with JDBC.
\end{achievements}

\employer{Citibank}{May 1999 - December 1999}{Data Processing Analyst}
\begin{achievements}
\item Handled corporate and private financial data.
\item User-level experience with IBM AIX.
\end{achievements}

\header{Education}

\schoolwithcourses{Shippensburg University}{Shippensburg, PA}{Bachelor of
  Science in Computer Science with a focus on Systems Programming, 1997-2001}

\schoolwithcourses{Shippensburg University}{Shippensburg, PA}{Masters of
  Science in Computer Science, 2002-2004}{27/30 credits attained (3.66 GPA)}

\header{Other Activities}
\begin{achievements}
\item Continuing education with development-related classes and workshops,
  attendance to developer conferences, and perpetual self-guided education.
\item Active Top Secret SCI with FS poly.
\item Contribution to various open-source projects, most recently starting a
  game server emulator project in Java and MySQL at:
  http://code.google.com/p/l1j-en/.
\item Publicly accessible code samples available at: http://github.com/bm3719.
\item Co-organizer of the National Capital Area Clojure Users Group:
  http://www.meetup.com/Cap-Clug/.
\end{achievements}

\end{document}
